# Appendices


## Appendix 1 - Current Canadian Inventories {-}


```{r echo=FALSE, message=FALSE, warning=FALSE}
z = read_csv("tables/appendix1.csv")
kable(z, caption="Current Canadian Inventories")
```


## Appendix 2 - Data Structure and Data Dictionary {-}

```{r echo=FALSE, message=FALSE, warning=FALSE}
z = read_csv("tables/appendix2.csv")
kable(z, caption="Data Structure and Data Dictionary")
```


## Appendix 3 - Stand Structure {-}

```{r echo=FALSE, message=FALSE, warning=FALSE}
z = read_csv("tables/appendix3.csv")
kable(z, caption="Stand Structure - Summary of Canadian Forest Inventories")
```


## Appendix 4 - Soil Moisture Regime {-}

```{r echo=FALSE, message=FALSE, warning=FALSE}
z = read_csv("tables/appendix4.csv")
kable(z, caption="Soil Moisture Regime - Summary of Canadian Forest Inventories and CAS Conversion")
```


## Appendix 5 - Crown Closure {-}

```{r echo=FALSE, message=FALSE, warning=FALSE}
z = read_csv("tables/appendix5.csv")
kable(z, caption="Crown Closure - Summary of Canadian Forest Inventories")
```


## Appendix 6 - Stand Height {-}

```{r echo=FALSE, message=FALSE, warning=FALSE}
z = read_csv("tables/appendix6.csv")
kable(z, caption="Stand Height - Summary of Canadian Forest Inventories")
```


## Appendix 7 - Species Composition {-}

```{r echo=FALSE, message=FALSE, warning=FALSE}
z = read_csv("tables/appendix7.csv")
kable(z, caption="Species Composition - Summary of Canadian Forest Inventories; and CAS Species Percent Translation (For Forest Inventories that do not provide species percent)")
```


## Appendix 8 - CAS Species List and Codes {-}


## Appendix 9 - CAS Generic Species Group List {-}


## Appendix 10 - Stand Origin (Age) {-}

Stand Origin (Age) - Summary of Canadian Forest Inventories


## Appendix 11 - Site Class and Site Index and CAS Conversion {-}


## Appendix 12 - Non-Forested, Non-Vegetated, and Unproductive Forest {-}

Non-Forested, Non-Vegetated, and Unproductive Forest - Summary of Canadian Forest Inventories; CAS Codes Non-Forested, Non-Vegetated, and Unproductive Forest Codes; and CAS Non-Forested, Non-Vegetated, and Unproductive Forest Conversion


## Appendix 13 - Disturbance History {-}

Disturbance History - Summary of Canadian Forest Inventories; CAS Disturbance History Codes; and Disturbance History CAS Conversion


## Appendix 14 - Wetland {-}

Wetland - Summary of Canadian Forest Inventories; CAS Wetland Conversion; and CAS Wetland Codes


## Appendix 15 - Procedures for CAS Wetland Derivation {-}


## Appendix 16 - Ecosite {-}

Ecosite - Summary of Canadian Forest Inventories


## Appendix 17 - Sample of Export Procedure {-}

