---  
title: "CAS Attributes"
output:  
  html_document:  
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    css: styles.css
---  

<br>

# What's new

<br>

# Overview

<br>

# Attributes

## cas_id

The cas_id attributes is used in 5 of the 6 CASFRI attribute tables and is only described here. This inventory has the following variations:

  * Header identifier: "AB06"
  * Source file name: "xxxxxGB_S21_TWP"
  * Name of mapsheet: trm_1
  * Object identifier: poly_num

## orig_stand_id {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
x = mutate(x, orig_stand_id = poly_num)
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["poly_num"], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["orig_stand_id"], graph.col=FALSE, max.distinct.values=99)
```

## stand_structure {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
x = mutate(x, stand_structure = if_else(str_trim(struc)=="", "-8888", struc))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["struc"], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["stand_structure"], graph.col=FALSE, max.distinct.values=99)
```

## num_of_layers {.tabset}

  * In the CAS_04, there are 2 values: 1 and 2; however I can't find the corresponding FRI attribute.

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["num_of_layers"], graph.col=FALSE, max.distinct.values=99)
```

## identification_id {.tabset}

  * The identification_id takes a value of 6.

```{r echo=TRUE, message=FALSE, warning=FALSE}
x = mutate(x, identification_id = 6)
```

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["identification_id"], graph.col=FALSE, max.distinct.values=99)
```

## map_sheet_id {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
x = mutate(x, map_sheet_id = trm)
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["trm"], graph.col=FALSE, max.distinct.values=10)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["map_sheet_id"], graph.col=FALSE, max.distinct.values=10)
```

## gis_area {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
x = mutate(x, gis_area= round(shape_area/10000,1))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["shape_area"], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["gis_area"], graph.col=FALSE, max.distinct.values=99)
```

## gis_perimeter {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
x = mutate(x, gis_perimeter = round(shape_length,0))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["shape_length"], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["gis_perimeter"], graph.col=FALSE, max.distinct.values=99)
```

## inventory_area {.tabset}

  * is this the same as GIS_AREA?

```{r echo=TRUE, message=FALSE, warning=FALSE}  
x = mutate(x, inventory_area = round(shape_area/10000,1))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["shape_area"], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["inventory_area"], graph.col=FALSE, max.distinct.values=99)
```

## photo_year {.tabset}

  * To do...

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["photo_year"], graph.col=FALSE, max.distinct.values=99)
```
