---  
title: "DST Attributes"
output:  
  html_document:  
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    css: styles.css
---  

<br>

# What's new

  * First version created on 2019-05-30

<br>

# Overview

<br>

# Attributes

## dist_1 {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}
friList = c('BU','CC','CL','PL','SC','SN','ST','TH')
casList = c('BU','CO','OT','SI','SI','DT','OT','SI')
x = mutate(x, dist_1=case_when(
    is.na(mod1) ~ "NULL_VALUE",
    str_trim(mod1)=="" ~ "EMPTY_STRING",
    !mod1 %in% friList ~ "NOT_IN_SET",
    TRUE ~ mapvalues(mod1, friList, casList)))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["mod1"], graph.col=FALSE, max.distinct.values=20)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["dist_1"], graph.col=FALSE, max.distinct.values=20)
```

## dist_yr_1 {.tabset}

  * what should a value of "0" be coded as?

```{r echo=TRUE, message=FALSE, warning=FALSE}
x = mutate(x, dist_yr_1=case_when(
    is.na(mod1_yr) ~ as.integer(-8888),
    mod1_yr==0 ~ as.integer(0), # NOT SURE WHAT THIS SHOULD BE?
    TRUE ~ mod1_yr))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["mod1_yr"], graph.col=FALSE, max.distinct.values=101)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x$dist_yr_1, graph.col=FALSE, max.distinct.values=101)
```

## dist_ext_upper_1, dist_ext_lower_1 {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}
friList = c(1,2,3,4,5)
casListUpper = c(25,50,75,95,100)
casListLower = c(1,26,51,76,96)
x = mutate(x, 
    dist_ext_upper_1=case_when(
    is.na(mod1_ext) ~ as.integer(-8888),
    mod1_ext==0 ~ as.integer(0), # NOT SURE WHAT THIS SHOULD BE?
    TRUE ~ as.integer(mapvalues(mod1_ext, friList, casListUpper))),
    dist_ext_lower_1=case_when(
    is.na(mod1_ext) ~ as.integer(-8888),
    mod1_ext==0 ~ as.integer(0), # NOT SURE WHAT THIS SHOULD BE?
    TRUE ~ as.integer(mapvalues(mod1_ext, friList, casListLower)))
    )
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["mod1_ext"], graph.col=FALSE, max.distinct.values=101)
```

### CASFRI (lower)

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x$dist_ext_lower_1, graph.col=FALSE, max.distinct.values=101)
```

### CASFRI (upper)

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x$dist_ext_upper_1, graph.col=FALSE, max.distinct.values=101)
```

## dist_2 {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}
friList = c('BU','CC','CL','PL','SC','SN','ST','TH')
casList = c('BU','CO','OT','SI','SI','DT','OT','SI')
x = mutate(x, dist_2=case_when(
    is.na(mod2) ~ "NULL_VALUE",
    str_trim(mod2)=="" ~ "EMPTY_STRING",
    !mod1 %in% friList ~ "NOT_IN_SET",
    TRUE ~ mapvalues(mod2, friList, casList)))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["mod2"], graph.col=FALSE, max.distinct.values=20)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["dist_2"], graph.col=FALSE, max.distinct.values=20)
```

## dist_year_2 {.tabset}

  * what should a value of "0" be coded as?

```{r echo=TRUE, message=FALSE, warning=FALSE}
x = mutate(x, dist_yr_2=case_when(
    is.na(mod2_yr) ~ as.integer(-8888),
    mod2_yr==0 ~ as.integer(0), # NOT SURE WHAT THIS SHOULD BE?
    TRUE ~ mod2_yr))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["mod2_yr"], graph.col=FALSE, max.distinct.values=101)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x$dist_yr_2, graph.col=FALSE, max.distinct.values=101)
```

## dist_ext_upper_1, dist_ext_lower_1 {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}
friList = c(1,2,3,4,5)
casListUpper = c(25,50,75,95,100)
casListLower = c(1,26,51,76,96)
x = mutate(x, 
    dist_ext_upper_2=case_when(
    is.na(mod2_ext) ~ as.integer(-8888),
    mod2_ext==0 ~ as.integer(0), # NOT SURE WHAT THIS SHOULD BE?
    TRUE ~ as.integer(mapvalues(mod2_ext, friList, casListUpper))),
    dist_ext_lower_2=case_when(
    is.na(mod2_ext) ~ as.integer(-8888),
    mod2_ext==0 ~ as.integer(0), # NOT SURE WHAT THIS SHOULD BE?
    TRUE ~ as.integer(mapvalues(mod2_ext, friList, casListLower)))
    )
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["mod2_ext"], graph.col=FALSE, max.distinct.values=101)
```

### CASFRI (lower)

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x$dist_ext_lower_2, graph.col=FALSE, max.distinct.values=101)
```

### CASFRI (upper)

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x$dist_ext_upper_2, graph.col=FALSE, max.distinct.values=101)
```

## dist_3 {.tabset}

  * not in AB06
  * value = ""-8888" in cas04

## dist_yr_3 {.tabset}

  * value = -8888 in cas04

## dist_ext_upper_3, dist_ext_lower_3 {.tabset}

  * not in AB06
  * value = -8888 in cas04

## layer {.tabset}

  * value = 1 in cas04
