---  
title: "ECO Attributes"
output:  
  html_document:  
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    css: styles.css
---  

<br>

# What's new

  * Version 1 created on 2019-05-30

<br>

# Overview

<br>

# Attributes

  * The first four attributes are created from several AB inventory attributes: crownclose, moisture, sp1, sp1_percntcnt, sp2, nonfor_veg, nat_nonveg

```{r echo=TRUE, message=FALSE, warning=FALSE}
x = mutate(x, 

  # Initialize CAS attributes
  wetland_type="NULL_VALUE", wet_veg_cover="NULL_VALUE", wet_landform_mod="NULL_VALUE", wet_local_mod="NULL_VALUE",

  wetland = case_when(
    moisture=="w" & !is.na(nonfor_veg) ~ "NULL_VALUE",
    moisture=="w" & nonfor_veg %in% c("SO","SC") ~ "SONS",
    moisture=="w" & nonfor_veg %in% c("HG","HF") ~ "MONG",
    moisture=="w" & nonfor_veg=="BR" ~ "FONG",
    moisture=="w" & nat_nonveg=="NWB" ~ "SONS",
    moisture %in% c("a","d","m") & (sp1=="LT" | sp2=="LT") & crownclose %in% c("A","B") ~ "FTNN",
    moisture %in% c("a","d","m") & (sp1=="LT" | sp2=="LT") & crownclose=="C" ~ "STNN",
    moisture %in% c("a","d","m") & (sp1=="LT" | sp2=="LT") & crownclose=="D" ~ "SFNN",
    moisture %in% c("a","d","m") & (sp1=="SB" & sp1_percnt==100) & crownclose %in% c("A","B") ~ "BTNN",
    moisture %in% c("a","d","m") & (sp1=="SB" & sp1_percnt==100) & crownclose=="C" ~ "STNN",
    moisture %in% c("a","d","m") & (sp1=="SB" & sp1_percnt==100) & crownclose=="D" ~ "SFNN",
    moisture %in% c("a","d","m") & ((sp1=="SB" | sp1=="FB") & !sp2=="LT") & crownclose %in% c("A","B","C") ~ "STNN",
    moisture %in% c("a","d","m") & ((sp1=="SB" | sp1=="FB") & !sp2=="LT") & crownclose=="D" ~ "SFNN",
    moisture %in% c("a","d","m") & sp1 %in% c("BW","PB") & crownclose %in% c("A","B","C") ~ "STNN",
    moisture %in% c("a","d","m") & sp1 %in% c("BW","PB") & crownclose=="D" ~ "SFNN",
    TRUE ~ "NULL_VALUE"),
  
  # Extract from wetland:
  wetland_type = if_else(wetland=="NULL_VALUE", "NULL_VALUE", substr(wetland,1,1)),
  wet_veg_cover = if_else(wetland=="NULL_VALUE", "NULL_VALUE", substr(wetland,2,2)),
  wet_landform_mod = if_else(wetland=="NULL_VALUE", "NULL_VALUE", substr(wetland,3,3)),
  wet_local_mod = if_else(wetland=="NULL_VALUE", "NULL_VALUE", substr(wetland,4,4))

)
```

## wetland_type {.tabset}

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["wetland_type"], graph.col=FALSE)
```

## wet_veg_cover {.tabset}

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["wet_veg_cover"], graph.col=FALSE)
```

## wet_landform_mod {.tabset}

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["wet_landform_mod"], graph.col=FALSE)
```

## wet_local_mod {.tabset}

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["wet_local_mod"], graph.col=FALSE)
```

## eco_site {.tabset}

  * Is this used for this inventory

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["eco_site"], graph.col=FALSE, max.distinct.values=20)
```
