---  
title: "ECO Attributes"
output:  
  html_document:  
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    css: styles.css
---  

<br>

# What's new

  * All ECO attributes are now ready for review. [2019-05-15]
  * eco_site is ready to reviewed. The other attributes should be ready soon. [2019-05-14]

<br>

# Overview

  * See comments under individual attribute heading

<br>

# Attributes

  * The first four attributes are created from several BC inventory attributes: non_productive_descriptor_cd, non_forest_descriptor, land_cover_class_cd_1, soil_moisture_regime_1, species_cd_1, species_pct_1, species_cd_2, crown_closure, and proj_height_1.

```{r echo=TRUE, message=FALSE, warning=FALSE}
x = mutate(x, 

  # Initialize CAS attributes
  wetland_type="NULL_VALUE", wet_veg_cover="NULL_VALUE", wet_landform_mod="NULL_VALUE", wet_local_mod="NULL_VALUE",

  # Process where inventory_standard_cd=="F"
  ##########################################
  wetland = case_when(
    inventory_standard_cd=="F" & species_cd_1 %in% c("SF","CW","YC") & non_productive_descriptor_cd=="S" ~ "STNN",
    inventory_standard_cd=="F" & species_cd_1 %in% c("SF","CW","YC") & non_productive_descriptor_cd=="NP" ~ "STNN",
    inventory_standard_cd=="F" & non_forest_descriptor=="NPBR" ~ "STNN",
    inventory_standard_cd=="F" & non_forest_descriptor=="S" ~ "SONS",
    inventory_standard_cd=="F" & non_forest_descriptor=="MUSKEG" ~ "STNN",
    TRUE ~ "NULL_VALUE"),

  # Process where inventory_standard_cd = "V" or "I"
  ##################################################
  wetland = case_when(
    inventory_standard_cd %in% c("V","I") & land_cover_class_cd_1=="W" ~ "W---",
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & species_cd_1=="SB" & species_pct_1==100 & crown_closure==50 & proj_height_1==12 ~ "BTNN",
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & species_cd_1 %in% c("SB","LT") & species_pct_1==100 & crown_closure>=50 & proj_height_1>=12 ~ "STNN",
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & species_cd_1 %in% c("SB","LT") & species_cd_2 %in% c("SB","LT") & crown_closure>=50 & proj_height_1>=12 ~ "STNN",
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & species_cd_1 %in% c("EP","EA","CW","YR","PI") ~ "STNN",
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & species_cd_1 %in% c("SB","LT") & species_cd_2 %in% c("SB","LT") & crown_closure<50 ~ "FTNN",
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & species_cd_1=="LT" & species_pct_1==100 & proj_height_1<12 ~ "FTNN",
    TRUE ~ wetland),

  wetland = case_when(
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & land_cover_class_cd_1 %in% c("ST","SL") ~ "SONS",
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & land_cover_class_cd_1 %in% c("HE","HF","HG") ~ "MONG",
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & land_cover_class_cd_1 %in% c("BY","BM") ~ "FONN", 
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & land_cover_class_cd_1=="BL" ~ "BONN",
    inventory_standard_cd %in% c("V","I") & soil_moisture_regime_1 %in% c(7,8) & land_cover_class_cd_1=="MU" ~ "TMNN",
    TRUE ~ wetland),
  
  # Extract from wetland:
  wetland_type = if_else(wetland=="NULL_VALUE", "NULL_VALUE", substr(wetland,1,1)),
  wet_veg_cover = if_else(wetland=="NULL_VALUE", "NULL_VALUE", substr(wetland,2,2)),
  wet_landform_mod = if_else(wetland=="NULL_VALUE", "NULL_VALUE", substr(wetland,3,3)),
  wet_local_mod = if_else(wetland=="NULL_VALUE", "NULL_VALUE", substr(wetland,4,4))

)
```

## wetland_type {.tabset}

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["wetland_type"], graph.col=FALSE)
```

## wet_veg_cover {.tabset}

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["wet_veg_cover"], graph.col=FALSE)
```

## wet_landform_mod {.tabset}

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["wet_landform_mod"], graph.col=FALSE)
```

## wet_local_mod {.tabset}

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["wet_local_mod"], graph.col=FALSE)
```

## eco_site {.tabset}

  * concatenated from bec_zone_code, bec_subzone, bec_variant, bec_phase, site_position_meso
  * add a "." between attributes and "" if attribute is null

```{r echo=TRUE, message=FALSE, warning=FALSE}  
x = mutate(x,
    eco_site = if_else(is.na(bec_zone_code), "", bec_zone_code),
    eco_site = if_else(is.na(bec_subzone), paste0(eco_site,"."), paste0(eco_site,".",bec_subzone)),
    eco_site = if_else(is.na(bec_variant), paste0(eco_site,"."), paste0(eco_site,".",bec_variant)),
    eco_site = if_else(is.na(bec_phase), paste0(eco_site,"."), paste0(eco_site,".",bec_phase)),
    eco_site = if_else(is.na(site_position_meso), paste0(eco_site,"."), paste0(eco_site,".",site_position_meso)))
```

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["eco_site"], graph.col=FALSE, max.distinct.values=20)
```
