---  
title: "ECO Attributes"
output:  
  html_document:  
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    css: styles.css
---  

<br>

# What's new

May 14, 2019

  * eco_site is ready to reviewed. The other attributes should be ready soon.

<br>

# Overview

  * See comments under individual attribute heading

## wetland_type {.tabset}


```{r echo=TRUE, message=FALSE, warning=FALSE}
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=20)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["wetland_type"], graph.col=FALSE, max.distinct.values=20)
```

## wet_veg_cover {.tabset}

### RAWFRI

### CASFRI

## wet_landform_mod {.tabset}

### RAWFRI

### CASFRI

## wet_local_mod {.tabset}

### RAWFRI

### CASFRI

## eco_site {.tabset}

  * concatenated from bec_zone_code, bec_subzone, bec_variant, bec_phase, site_position_meso
  * add a "." between attributes and "" if attribute is null

```{r echo=TRUE, message=FALSE, warning=FALSE}  
x = mutate(x,
    eco_site = if_else(is.na(bec_zone_code), "", bec_zone_code),
    eco_site = if_else(is.na(bec_subzone), paste0(eco_site,"."), paste0(eco_site,".",bec_subzone)),
    eco_site = if_else(is.na(bec_variant), paste0(eco_site,"."), paste0(eco_site,".",bec_variant)),
    eco_site = if_else(is.na(bec_phase), paste0(eco_site,"."), paste0(eco_site,".",bec_phase)),
    eco_site = if_else(is.na(site_position_meso), paste0(eco_site,"."), paste0(eco_site,".",site_position_meso)))
```

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
dfSummary(x["eco_site"], graph.col=FALSE, max.distinct.values=20)
```
