---  
title: "CAS Attributes"
output:  
  html_document:  
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    css: styles.css
---  

<br>

# What's new

<br>

# Overview

<br>

# Attributes

## cas_id

The cas_id attributes is used in 5 of the 6 CASFRI attribute tables and is only described here. This inventory has the following variations:

  * Header identifier: "NB01"
  * Source file name: "xxFOREST_NONFOR"
  * Name of mapsheet: "xxxxxxxxxx"
  * Object identifier: stdlab

## orig_stand_id {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["orig_stand_id"], graph.col=FALSE, max.distinct.values=99)
```

## stand_structure {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["stand_structure"], graph.col=FALSE, max.distinct.values=99)
```

## num_of_layers {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["num_of_layers"], graph.col=FALSE, max.distinct.values=99)
```

## identification_id {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}
```

### RAWFRI

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["identification_id"], graph.col=FALSE, max.distinct.values=99)
```

## map_sheet_id {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=10)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["map_sheet_id"], graph.col=FALSE, max.distinct.values=10)
```

## gis_area {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["gis_area"], graph.col=FALSE, max.distinct.values=99)
```

## gis_perimeter {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["gis_perimeter"], graph.col=FALSE, max.distinct.values=99)
```

## inventory_area {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["inventory_area"], graph.col=FALSE, max.distinct.values=99)
```

## photo_year {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["photo_year"], graph.col=FALSE, max.distinct.values=99)
```
