---  
title: "NFL Attributes"
output:  
  html_document:  
    code_folding: hide
    toc: true
    toc_float:
      collapsed: false
    css: styles.css
---  

<br>

# What's new

<br>

# Overview

  * Overstory: nonfor_veg, (nonforvecl?), anthro_veg, anth_noveg, nat_nonveg
  * Understory: nonforvegu, nforvegclu, us_anthveg, us_annoveg, us_natnveg

<br>

# Attributes

```{r echo=TRUE, message=FALSE, warning=FALSE}  
#friList = c('??','WL','NWL','WR','NWR','??','MC','MM','MR','NMM','NMR','MG','WI','NWI','??','MB','NMB','NMC','??','MS','NMS','WF','NWF','??','??')
#casList = c('AP','LA','LA','RI','RI','OC','RK','RK','RK','RK','RK','SA','SI','SI','SL','EX','EX','EX','BE','WS','WS','FL','FL','IS','TF')
#x = mutate(x, nat_non_veg=if_else(nat_nonveg==" ","NULL_VALUE", if_else(!nat_nonveg==" " & !nat_nonveg %in% friList, "NOT_IN_SET", mapvalues(nat_nonveg, friList, casList))))
```

## nat_non_veg {.tabset}

### RAWFRI

```{r echo=TRUE, message=FALSE, warning=FALSE}  
#dfSummary(x["nat_nonveg"], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["nat_non_veg"], graph.col=FALSE, max.distinct.values=99)
```

## non_for_anth {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}
#friList = c('AII','AIM','AIG','AIE','II','IM','IG','IE','CIP','CIW','AIH','IP','IW','IH','AIW','IW','CA','CP','CPR','A','P','PR','ASC','ASR','AIF','SC','SR','IF','??','??  ','CIU','AIU','IU','AIL')
#casList = c('IN','IN','IN','IN','IN','IN','IN','IN','FA','FA','FA','FA','FA','FA','FA','FA','CL','CL','CL','CL','CL','CL','SE','SE','SE','SE','SE','SE','LG','BP','OT','OT','OT','OT')
#x = unite(x, anth_veg_non, c(anthro_veg, anth_noveg), sep="", remove=FALSE) %>% mutate(anth_veg_non = str_trim(anth_veg_non))
#x = mutate(x, non_for_anth=if_else(anth_veg_non=="","NULL_VALUE", if_else(!anth_veg_non=="" & !anth_veg_non %in% friList, "NOT_IN_SET", mapvalues(anth_veg_non, friList, casList))))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["anthro_veg"], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["non_for_anth"], graph.col=FALSE, max.distinct.values=99)
```

## non_for_veg {.tabset}

  * Check AB perl code for SC, SO

```{r echo=TRUE, message=FALSE, warning=FALSE}  
#friList = c('??','AS','HF','??','HG','AIL','IL','BR','??','??','SC','SO')
#casList = c('ST','SL','HF','HE','HG','HG','HG','BR','OM','TN','SC','SO')
#x = mutate(x, nat_non_veg=if_else(nonfor_veg=="","NULL_VALUE", if_else(!nonfor_veg=="" & !nonfor_veg %in% friList, "NOT_IN_SET", mapvalues(nonfor_veg, friList, casList))))
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["nonfor_veg"], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["non_for_veg"], graph.col=FALSE, max.distinct.values=99)
```

## soil_moist_reg {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```
### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["nfl_soil_moist_reg"], graph.col=FALSE, max.distinct.values=99)
```

## structure_per {.tabset}

### RAWFRI

### CASFRI

## crown_closure_upper {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["nfl_crown_closure_upper"], graph.col=FALSE, max.distinct.values=99)
```

## crown_closure_lower {.tabset}


```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["nfl_crown_closure_lower"], graph.col=FALSE, max.distinct.values=99)
```

## height_upper {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["nfl_height_upper"], graph.col=FALSE, max.distinct.values=99)
```

## height_lower {.tabset}

```{r echo=TRUE, message=FALSE, warning=FALSE}  
```

### RAWFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x[""], graph.col=FALSE, max.distinct.values=99)
```

### CASFRI

```{r echo=FALSE, message=FALSE, warning=FALSE}  
#dfSummary(x["nfl_height_lower"], graph.col=FALSE, max.distinct.values=99)
```
