---
title: ""
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    css: style.css
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tidyverse)
x = read_csv("tables.csv")
y = unique(x$Attribute)
i = 1
```

<center><br><br><b><font size=+2>COMMON ATTRIBUTE SCHEMA (CAS)<br>FOR FOREST INVENTORIES ACROSS CANADA</font></b>
<br><br><br>
Prepared by: John A. Cosco, Chief Inventory Forester, February 2011<br>
Revised by: The CASFRI Project Team, February 2019</center>
<br><br>

# Introduction {#intro}

Canada's vast boreal ecosystem hosts one of the most diverse bird communities in North America. Development pressure within the boreal region is on the increase, and there is an urgent need to understand the impact of changing habitats on boreal bird populations and to
make sound management decisions. The Boreal Avian Modeling Project was initiated to help address the lack of basic information on boreal birds and their habitats across boreal forests in Canada. The need to effectively manage bird species and their habitats has resulted in the effort to collect and gather data across Canada to develop models that will predict bird abundance and distribution, and that will clarify population and habitat associations with climate and land cover.

Current national databases developed from satellite-based products using biophysical variables have limited application at regional levels because many bird species are sensitive to variation in canopy tree species composition, height, and age; vegetation attributes that satellite-based products cannot measure. Because satellite-based land cover maps lack the thematic detail needed to model the processes of stand growth, succession, and regeneration, avian habitat models derived from satellite land cover data cannot be used to link forest management actions to the desired biotic indicators at the scale of forest tenure areas.

Digital forest inventory data can overcome many of the deficiencies identified with satellitebased land cover data. These data exist for most operational and planned commercial forest tenures in the Canadian boreal forest; however, differences among data formats, attributes, and standards across the various forest inventories make it difficult to develop models that are comparable and can be consistently applied across regions. To do so, it is necessary to address the variation between different forest inventories and bring all available inventories into one
explicitly defined database where attributes are consistently defined without loss of precision. The starting point is to review all forest inventory classifications and develop a set of common attributes. This document addresses the inventory review developed for the Boreal Avian Monitoring Project; this review is called the Common Attribute Schema (CAS).

# Common Attribute Schema

The common attribute schema (CAS) is a comprehensive attribute classification suitable for avian habitat modeling. Its development requires the selection of vegetation cover attributes useful for avian habitat modeling, and the assignment of common codes for each attribute that are broad enough to capture all relevant existing forest inventory attributes. CAS attributes represent the most common attributes that are consistently recorded in forest inventories across Canada including: stand structure (layers), moisture regime, crown closure, species composition, height, age (origin), site class or site index, non-forested cover types, non-vegetated cover types, and disturbance history. CAS also includes two attributes of ecological interest: ecosite and wetland. These two attributes are not common to most forest inventories across Canada; however, these attributes are considered important for avian habitat models and can possibly be acquired from other sources or partially or wholly derived from other attributes.

Development of the CAS attribute codes and rule sets for inventory attribute code conversion to CAS codes required an extensive review of previous and current inventory standards and specifications across Canada. Gillis and Leckie<sup>1</sup> provided a good starting point for review of previous inventory standards. More current and other inventory standards and documents are listed in the bibliography. A summary of recent or current inventories across Canada are presented in Appendix 1. These inventories are the most likely sources for data that can contribute to the avian bird modeling project.

Based on the review, detailed tables were produced to summarize each inventory standard by province and territory. Two national parks, Wood Buffalo and Prince Albert are included. Conversion rule sets were then produced as part of the detailed tables to identify how each province or territory inventory attribute codes translate into CAS attribute codes. Detailed tables and conversion rule sets for each CAS attribute are presented in Appendices noted in the appropriate sections of this document.

Although many CAS attributes have a one-to-one conversion, not all do; some are identified by an interval or class that has an upper and lower bound (lower bound is > and the upper bound is <). Interval coding for height, crown closure, age, and similar quantitative attributes is a unique feature of CAS. Crown closure, height, age, and disturbance extent use bounds to define an attribute class. For example, the CAS captures crown closure as an interval providing two values, the lower bound and upper bound. In the Alberta Vegetation Inventory, crown closure is captured in four cover classes: A, B, C and D, while the British Columbia Vegetation Resource Inventory captures crown closure as values ranging from 1 to 100 to the nearest 1 percent. In CAS, an Alberta "B" - value would be represented as an interval: 31 for the lower bound and 50 for the upper bound. A British Columbia crown closure value of 36 would be represented as a CAS value of 36 for both the lower and upper bounds. All of the information contained in the original inventories is preserved and the attributes are not converted to a common resolution or set of values.

Attributes for CAS are stored in six attribute files to facilitate conversion and translation:

1)	Header (HDR) attributes - values assigned to all polygons based on provenance or reference information;

2)	CAS Base Polygon (CAS) attributes - values that identify a polygon and provide a link between the CAS polygon and the original inventory polygon;

3)	Forest-Level (LYR) attributes - values that pertain to the polygon for productive and non-productive forest land;

4)	Non-Forest Land (NFL) attributes - values that pertain to naturally non-vegetated, non-forest anthropogenic, and non-forest vegetated land;

5)	Disturbance history (DST) attributes - values that pertain to any disturbance that has occurred in a polygon including type, year, and extent; and

6)	Ecological specific (ECO) attributes - values representing ecosites and wetlands.

The main body of this report (Sections 2.1 through 2.3 and Section 3) defines each of the six attribute categories and tabulates the attributes and their characteristics. A summary of the data structure and data dictionary is presented in Appendix 2.

Each inventory data base has a unique data structure. A conversion procedure must be documented describing how to load the source inventory into CAS. A sample procedure is presented in Appendix 16.

<sup>1</sup> Gillis, M.D.; Leckie, D.G. 1993. Forest Inventory Mapping Procedures Across Canada. Petawawa National Forestry Institute, Information Report PI-X-114.

## Header Information

Header information is a primary element of CAS. Header information identifies the source data set including jurisdiction, spatial reference, ownership, tenure type, inventory type, inventory version, inventory start and finish date and the year of acquisition for CAS. These attributes are detailed on the following pages.

### Jurisdiction

Jurisdiction identifies the province or territory from which the inventory data came.

```{r echo=FALSE, message=FALSE}
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

### Spatial Reference

Spatial reference describes the reference frame for, and the means to encode, coordinates in the data set including a coordinate system, projection, and datum. Coordinates can be referenced to any desired geographic grid. The coordinate system is a method of representing points in a space of given dimensions by coordinates to establish position. A projection is a systematic construction of lines drawn on a plane surface representative of and corresponding to the meridians and parallels of the curved surface of the earth. A datum is the geodetic datum specifying that coordinate system in which horizontal control points are located. The North American Datum (NAD) of 1983 is the current datum used in Canada. Some inventories may use the NAD of 1927.

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

### Ownership		

Ownership identifies who owns the inventory data, who owns the land that the inventory covers, and degree of permission to which the data can be used. Ownership of the inventory can be federal, provincial, territory, industry, private, or First Nation. Ownership of the land is identified as being crown, private, military, or First Nation. Permission identifies whether the use of the data is unrestricted, restricted or limited.

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

### Tenure Type

Tenure type identifies the kind of agreement or license under which the inventory was done. Various tenure types exist across Canada. The most common types are included in the list below; any others are to be coded as "other".

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

### Inventory Metadata

Inventory metadata provides general information with regard to a particular forest or vegetation inventory. The inventory type identifies the kind of inventory that was produced for an area. The name, abbreviation, or acronym usually becomes the name used to identify an inventory. For example, Alberta had a series of successive forest inventories called Phase 1, Phase 2, and Phase 3. As inventories became more inclusive of attributes other than just the trees, they became known as vegetation inventories, for example, the Alberta Vegetation Inventory or AVI. The inventory type along with a version number usually identifies an inventory.

The inventory version identifies the standards used to produce a consistent inventory, usually across large landbases and for a relatively long period of time. Inventory Reference Year identifies the year the inventory done. An inventory can take several years to complete; therefore, Reference Year Minimum and Maximum dates are included to identify the interval for when the inventory was completed. In some cases inventory reference year and air photo year will be the same. Several years of successive or periodic acquisition are possible; therefore, a minimum and a maximum year are recorded. Inventory Start and Finish Year identifies the year the inventory was started and finished. Year of Update indicates the year that an inventory was updated.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

### CAS Data Acquisition

CAS data acquisition identifies the year that the inventory was acquired for CAS. A unique number is assigned to each inventory for purposes of CAS identification.

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

## CAS Base Polygon Attributes

The CAS base polygon data provides polygon specific information and links the original inventory polygon ID to the CAS ID. Identification attributes include original stand ID, CAS Stand ID, Mapsheet ID, and Identification ID. Polygon attributes include polygon area and polygon perimeter. Inventory Reference Year, Photo Year, and Administrative Unit are additional identifiers.


### Polygon Identification			

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Polygon Area and Perimeter			

Each polygon area and perimeter is recorded.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Year of Aerial Photography

Photo Year is the year in which the inventory was considered initiated and completed. An inventory can take several years to complete; therefore, Photo Year Minimum and Maximum dates are included to identify the interval for when the inventory was completed. In some cases inventory reference year and air photo year are the same. Several years of successive or periodic acquisition are possible; therefore, a minimum and a maximum year are recorded.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Administration Unit

Administration unit identifies any inventory sub-unit boundaries that exist within an inventory. Sub- unit boundaries can possibly split a polygon; therefore, this CAS attribute is applied at the CAS base polygon level. Two administration unit (possibly hierarchical) levels of organization are identified, such as Forest Management Units (FMUs) and Working Circle (WC) or Compartment (CMPT). Their interpretation is source-data-set explicit.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

## CAS Forest and Non-Forest Attributes

### Stand Structure

Structure is the physical arrangement or vertical pattern of organization of the vegetation within a polygon. A stand can be identified as single layered, multilayered, complex, or horizontal. A single layered stand has stem heights that do not vary significantly and the vegetation has only one main canopy layer.

A multilayered stand can have several distinct layers and each layer is significant, has a distinct height difference, and is evenly distributed. Generally the layers are intermixed and when viewed vertically, one layer is above the other. Layers can be treed or non-treed. Up to 9 layers are allowed; most inventories recognize only one or two layers. The largest number of layers recognized is in the British Columbia VRI with 9 followed by Saskatchewan SFVI with 7 and Manitoba FLI with 5. Each layer is assigned an independent description with the tallest layer described in the upper portion of the label. The number of layers and a ranking of the layers can also be assigned. Some inventories (e.g. Saskatchewan UTM, Quebec TIE, Prince Edward Island, and Nova Scotia) can imply that a second layer exists; however, the second layer is not described or only a species type is indicated.

Complex layered stands exhibit a high variation in tree heights. There is no single definitive forested layer as nearly all height classes (and frequently ages) are represented in the stand. The height is chosen from a stand midpoint usually followed by a height range.

Horizontal structure represents vegetated or non-vegetated land with two or more homogeneous strata located within other distinctly different homogeneous strata within the same polygon but the included strata are too small to map separately based on minimum polygon size rules. This attribute is also used to identify multi- label polygons identified in biophysical inventories such as Wood Buffalo National Park and Prince Albert National Park. The detailed table for stand structure is presented in Appendix 3.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Structure Percent or Range

Stand Structure Percent or Range is assigned when a complex or horizontal structured polygon is identified. Stand structure percent is used with horizontal stands and identifies the percentage of stand area, assigned in 10% increments, attributed by each stratum within the entire polygon and must add up to 100%. Any number of horizontal strata can be described per horizontal polygon.

Stand Structure Range is used with complex stands and represents the height range (m) around the stand midpoint. For example, height range 6 means that the range around the midpoint height is 3 meters above and 3 meters below the midpoint.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Number of Layers

Number of Layers is an attribute related to stand structure and identifies how many layers have been identified for a particular polygon.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Layer		

Layer is an attribute related to stand structure that identifies which layer is being referred to in a multi-layered stand. The layer identification creates a link between each polygon attribute and the corresponding layer. Layer 1 will always be the top (uppermost) layer in the stand sequentially followed by Layer 2 and so on.

The maximum number of layers recognized is nine. The uppermost layer may also be a veteran (V)	layer. A veteran layer refers to a treed layer with a crown closure of 1 to 5 percent and must occur with at least one other layer; it typically includes the oldest trees in a stand.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Layer Rank			

Layer Rank value is an attribute related to stand structure and refers to layer importance for forest management planning, operational, or silvicultural purposes. When a Layer Rank is not specified, layers can be sorted in order of importance by layer number.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Soil Moisture Regime

Soil moisture regime describes the available moisture supply for plant growth over a period of several years. Soil moisture regime is influenced by precipitation, evapotranspiration, topography, insolation, ground water, and soil texture. The CAS soil moisture regime code represents the similarity of classes across Canada. The detailed soil moisture regime table and CAS conversion is presented in Appendix 4.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Crown Closure

Crown closure is an estimate of the percentage of ground area covered by vertically projected tree crowns, shrubs, or herbaceous cover. Crown closure is usually estimated independently for each layer. Crown closure is commonly represented by classes and differs across Canada; therefore, CAS recognizes an upper and lower percentage bound for each class. The detailed crown closure table is presented in Appendix 5.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Height		

Stand height is based on an average height of leading species of dominant and co-dominant heights of the vegetation layer and can represent trees, shrubs, or herbaceous cover. Height can be represented by actual values or by height class and its representation is variable across Canada; therefore, CAS will use upper and lower bounds to represent height. The detailed height table is presented in Appendix 6.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Species Composition

Species composition is the percentage of each tree species represented within a forested polygon by layer. Species are listed in descending order according to their contribution based on crown closure, basal area, or volume depending on the province or territory. A total of ten species can be used in one label. The CAS attribute will capture estimation to the nearest percent; however, most inventories across Canada describe species to the nearest 10% (in actual percent value or multiples of 10). Species composition for each forest stand and layer must sum to 100%.

The detailed table for species composition is presented in Appendix 7. Some inventories (Alberta Phase 3, Saskatchewan UTM, Quebec TIE, and Newfoundland, and National Parks) do not recognize a percentage breakdown of species but rather group species as contributing a major (greater than 26 percent) or minor (less than 26 percent) amount to the composition. Also included in Appendix 7 is a translation table that assigns a species composition percentage breakdown for those inventories that do not have a percentage breakdown.

CAS species codes are derived from the species‟ Latin name using the first four letters of the Genus and the first four letters of the Species unless there is a conflict, then the last letter of the species portion of the code is changed. Unique codes are required for generic groups and hybrids. A species list has been developed representing every inventory species identified across Canada including hybrids, exotics and generic groups (Appendix 8). Generic groups represent situations where species were not required to be recognized past the generic name or where photo interpreters could not identify an individual species. A list of species that is represented by the generic groups by province, territory, or Park has also been developed and is presented in Appendix 9.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Stand Origin

Stand origin is the average initiation year of codominant and dominant trees of the leading species within each layer of a polygon. Origin is determined either to the nearest year or decade. An upper and lower bound is used to identify CAS origin. The detailed stand origin table is presented in Appendix 10.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Site Class

Site class is an estimate of the potential productivity of land for tree growth. Site class reflects tree growth response to soils, topography, climate, elevation, and moisture availability. See Appendix 11 for the detailed site table.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Site Index	

Site Index is an estimate of site productivity for tree growth. It is derived for all forested polygons based on leading species, height, and stand age based on a specified reference age. Site index is not available for most inventories across Canada. See Appendix 11 for the detailed site table.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Unproductive Forest

Unproductive forest is forest land not capable of producing trees for forest operations. They are usually wetlands, very dry sites, exposed sites, rocky sites, higher elevation sites, or those sites with shallow or poor soils. The detailed table, CAS codes, and conversion rule sets are presented in Appendix 12.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Naturally Non Vegetated	

The Naturally Non-Vegetated class refers to land types with no vegetation cover. The maximum vegetation cover varies across Canada but is usually less than six or ten percent. The detailed table, CAS codes, and CAS conversion rule set are presented in Appendix 12.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Non-Vegetated Anthropogenic

Non-vegetated anthropogenic areas are influenced or created by humans. These sites may or may not be vegetated. The detailed table, CAS codes, and CAS conversion rule set are presented in Appendix 12.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Non-Forested Vegetated		

Non-forested vegetated areas include all natural lands that have vegetation cover with usually less than 10% tree cover. These cover types can be stand alone or used in multi-layer situations. The detailed table, CAS codes, and CAS conversion rule set are presented in Appendix 12.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Disturbance

Disturbance identifies the type of disturbance history that has occurred or is occurring within the polygon. The type of disturbance, the extent of the disturbance and the disturbance year, if known, may be recorded. The disturbance may be natural or human -caused. Up to three disturbance events can be recorded with the oldest event described first. Silviculture treatments have been grouped into one category and include any silviculture treatment or treatments recorded for a polygon. The detailed table, CAS codes, and CAS conversion rule set are presented in Appendix 13.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Disturbance Extent

Disturbance extent provides an estimate of the proportion of the polygon that has been affected by the disturbance listed. Extent codes and classes vary across Canada where they occur; therefore, CAS identifies upper and lower bounds for this category. Three disturbance extents can be identified, one for each disturbance event.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

### Disturbance Year

Disturbance year is the year a disturbance event occurred. The disturbance year may be unknown. Three disturbance years can be identified, one for each disturbance event.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

# Ecological Attributes

Ecological attributes are generally not included or are incompletely recorded in typical forest inventories across Canada. Two attributes have been included for CAS: ecosite and wetland. These attributes are to be translated or derived for CAS from other attributes whenever possible.

## Wetland

The wetland classification scheme used for CAS follows the classes developed by the National Wetlands Working Group<sup>2</sup> and modified by Vitt and Halsey<sup>3,4</sup>. The scheme was further modified to take into account coastal and saline wetlands. The CAS wetland attribute is composed of four parts: wetland class, wetland vegetation modifier, wetland landform modifier, and wetland local modifier.

Five major wetland classes are recognized based on wetland development from hydrologic, chemical, and biotic gradients that commonly have strong cross-correlations. Two of the classes; fen and bog, are peat-forming with greater than 40 cm of accumulated organics. The three non- peat forming wetland types are shallow open water, marsh (fresh or salt water), and swamp. A non-wetland class is also included. The Vegetation Modifier is assigned to a wetland class to describe the amount of vegetation cover. The Landform Modifier is a modifier label used when permafrost, patterning, or salinity are present. The Local Landform Modifier is a modifier label used to define the presence or absence of permafrost features or if vegetation cover is shrub or graminoid dominated.

The detailed wetland table, CAS code set, and CAS translation rule set are presented in Appendix 14. Not many forest inventories across Canada provide a wetland attribute. Some inventories have complete or partial wetland attributes while others will need to have wetland classes derived from other attributes or ecosite information. The level of wetland detail that is possible to describe from a particular inventory database is dependent on the attributes that already exist. A rule set for each province or territory that identifies a method to derive wetland attributes using forest attributes or ecosite data is presented in Appendix 15. The wetland derivation may not be complete nor will it always be possible to derive or record all four wetland attributes in the CAS database.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

<br>

<sup>2</sup>National Wetlands Working Group 1988. Wetlands of Canada. Ecological Land Classification Series No. 24.

<sup>3</sup>Alberta Wetland Inventory Standards. Version 1.0. June 1977. L. Halsey and D. Vitt.

<sup>4</sup> Alberta Wetland Inventory Classification System. Version 2.0. April 2004. Halsey, et. al.


## Ecosite

Ecosites are site-level descriptions that provide a linkage between vegetation and soil/moisture and nutrient features on the site. The detailed ecosite table is presented in Appendix 16. A common attribute structure for ecosite is not provided for CAS because ecosite is not available for most forest inventories across Canada nor can it be derived from existing attributes. An ecosite field is included in CAS to accommodate inventories that do include ecosite data. The original inventory attribute value is captured in CAS. For example some codes: Quebec = MS25S, Ontario = ES11 or 044 or S147N and Alberta = UFb1.2.

<br>

```{r echo=FALSE, message=FALSE}
i = i + 1
z = filter(x, Attribute==y[i]) %>% select(Description, AttributeValue)
names(z) = c(y[i], "Attribute Value")
kable(z)
```

# Bibliography

<b>British Columbia</b>

Ministry of Forests 1982. Forest and Range Inventory Manual, Chapter 3, Forest Classification.

Ministry of Forests 1992. Forest Inventory Manual. Volumes 1 - 5.

Resource Inventory Committee 2002. Vegetation Resources Inventory, Version 2.4. Photo Interpretation Procedures. Ministry of Sustainable Resource Management. Terrestrial Information Branch (http://www.for.gov.bc.ca/risc).

Sandvoss, M, B. McClymont and C. Farnden (compilers) 2005. A User's Guide to the Vegetation Resources Inventory. Timberline Forest Inventory Consultants.

<b>Alberta</b>

Alberta Department of Energy and Nat. Res. 1985. Alberta Phase 3 Forest Inventory: An Overview. Rep. No. I/86.

Alberta Department of Energy and Nat. Res. 1985. Alberta Phase 3 Inventory: Forest Cover Type Specifications. Rep. No. 58.

Alberta Environmental Protection 1991. Alberta Vegetation Inventory Standards Manual, Version 2.1. Resource Data Division. Data Acquisition Branch.

Alberta Sustainable Resource development. 2005. Alberta Vegetation Inventory Standards. Version 2.1.1 March 2005. Chapter 3 - Vegetation Inventory Standards and Data Model Documents. Resource Information Branch.

Halsey L. and D.H. Vitt. 1977 Alberta Wetland Inventory Standards. Version 1.0. June.

Halsey L., D.H. Vitt, D. Beilman, S. Crow, S. Meehelcic, and R. Wells. 2004. Alberta Wetland Inventory Classification System Version 2.0. Alberta Sustainable Resource Development, Resource Data Branch. Pub. No, T/031.

<b>Saskatchewan</b>

Lindenas, D.J. 1985. Specifications for the Interpretation and Mapping of Aerial Photographs in the Forest Inventory Section. Sask. Dept. Parks and Renew. Res. Internal Manual.

Saskatchewan Environment 2004. Saskatchewan Forest Vegetation Inventory, Version 4.0.

Forest Service. (www.se.gov.sk.ca/forests/forestmanagement/Sask_Leg_Manuals.htm.

<b>Manitoba</b>

Manitoba Conservation. Prior to 1992. Forest Inventory Manual 1.0 and 1.1. Forest Inventory and Resource Analysis.

Manitoba Conservation. 1992 - 1996. Forest Inventory Manual 1.2. Forest Inventory and Resource Analysis.

Manitoba Conservation. 1996 - 1997. Forest Inventory Manual 1.3. Forest Inventory and Resource Analysis.

Manitoba Conservation. 2001. Forest Lands Inventory Manual 1.1. Forest Inventory and Resource Analysis.

Louisiana Pacific Canada Ltd. 2004. FLI User Guide (Draft). Prepared by The Forestry Corp. Ontario

Ontario Ministry of Natural Resources. 1996. Specifications for Forest Resources Inventory Photo Interpretation. Updated Mar. 1996.

Ontario Ministry of Natural Resources. 2001. Specifications for Forest Resources Inventory Photo Interpretation. Updated Sept. 2001.

Ontario Ministry of Natural Resources. 2007. Ontario Forest Resources Inventory Photo Interpretation Specifications. Updated Dec_2007.

Ontario Ministry of Natural Resources. 2010. Ontario Forest Resources Inventory Photo Interpretation Specifications. Updated Dec_2010.

OMNR, April 2001. Forest Information Manual. Toronto: Queen's Printer for Ontario. 400 pp.

OMNR, April 2007. Forest Information Manual. Toronto: Queen's Printer for Ontario. 107 pp. (http://ontariosforests.mnr.gov.on.ca/ontariosforests.cfm)

Pikangikum First Nation. 2003. Whitefeather Forest FRI/FEC Procedures Manual. Internal Document prepared by Timberline Forest Inventory Consultants Ltd.

Eabametoong and Mishkeegogamang First Nation. 2007. FRI/FEC Procedures Manual. Internal Document prepared by Timberline Natural Resource Group Ltd.

<b>Quebec</b>

Foret Quebec. 2003. Normes de Cartographie Ecoforestiere. Troisieme Inventaire Ecoforestier. Ministere des Ressources Naturelles, de la Faune et des Parcs du Quebec. Direction des Inventaires Forestiers.

Foret Quebec. 2008. Norme de Stratification Ecoforestiere. Quatrieme Inventaire Ecoforestier.

Direction des Inventaires Forestiers.

<b>Prince Edward Island</b>

Prince Edward Island Dept. of Agric. and For. 2001. Photo Interpretation Specifications.

Province of Prince Edward Island. Natural Resources Division, Revised 2001.

<b>New Brunswick</b>

Dept. of Nat. Resources. 2005. New Brunswick Integrated Land Classification System. Forest Management Branch

<b>Nova Scotia</b>

Dept. of Nat. Resources 2006. Photo Interpretation Specifications. Forestry Division. Manual FOR 2006-1.

<b>Newfoundland and Labrador</b>

Dept. of Nat. Resources 2006. Photo Interpretation Procedures and Technical Specifications.

Forestry Services Branch.

<b>Yukon Territory</b>

Yukon Energy, Mines, and Resources. 2006. Yukon Vegetation Inventory Manual. Version 2.1.

Forest Management Branch.

<b>Northwest Territories</b>

Dept. of Energy and Natural Resources 2004. Northwest Territories Forest Vegetation Photo Interpretation, Transfer and Database Standards. Forest Resources, Forest Management Division.

Dept. of Energy and Natural Resources. 2006. Northwest Territories Forest Vegetation Inventory Standards with Softcopy Supplements, Version 3.0. Forest Resources, Forest Management Division.

<b>Prince Albert National Park</b>

Padbury, G.E., W.K. Head, and W.E. Souster. 1978. Biophysical Resource Inventory of Prince Albert National Park, Saskatchewan. Saskatchewan Institute of Pedology Publication S185, Saskatoon.

Fitzsimmons, M. 1998. Prince Albert National Park Forest Cover Data in Vector Format. http://daac.ornl.gov/boreas/STAFF/panpfcov/comp/PNP_For_Cov.txt

<b>Wood Buffalo National Park</b>

Air Photo Analysis Associates. 1979. Biophysical inventory of Wood Buffalo National Park.

Prepared for Department of Indian and Northern Affairs, Parks Canada. Prairie Region.

WBNPBiophysical. 2001. SMMS Metadata Report.

<b>General</b>

Gillis, M.D.; Leckie, D.G. 1993. Forest Inventory Mapping Procedures Across Canada.

Petawawa National Forestry Institute, Information Report PI-X-114.

Leckie D.G and Gillis M.D. 1995 Forest Inventory in Canada with emphasis on map production.

The Forestry Chronicle 71 (1): 74 - 88.

National Wetlands Working Group 1988. Wetlands of Canada. Ecological Land Classification Series No. 24.


# Appendices

The appendices are listed below and can be viewed or edited using the cas_appendices.xlsx workbook located in the github specifications folder.

  * Appendix 1	Current Canadian Inventories
  * Appendix 2	Data Structure and Data Dictionary
  * Appendix 3	Stand Structure - Summary of Canadian Forest Inventories
  * Appendix 4	Soil Moisture Regime - Summary of Canadian Forest Inventories and CAS Conversion
  * Appendix 5	Crown Closure - Summary of Canadian Forest Inventories
  * Appendix 6	Stand Height - Summary of Canadian Forest Inventories
  * Appendix 7a	Species Composition - Summary of Canadian Forest Inventories
  * Appendix 7b	CAS Species Percent Translation (For Forest Inventories that do not provide species percent)
  * Appendix 8	CAS Species List and Codes
  * Appendix 9	CAS Generic Species Group List
  * Appendix 10	Stand Origin (Age) - Summary of Canadian Forest Inventories
  * Appendix 11	Site Class and Site Index and CAS Conversion
  * Appendix 12a	Non-Forested, Non-Vegetated, and Unproductive Forest - Summary of Canadian Forest Inventories
  * Appendix 12b	CAS Codes Non-Forested, Non-Vegetated, and Unproductive Forest Codes
  * Appendix 12c	CAS Non-Forested, Non-Vegetated, and Unproductive Forest Conversion
  * Appendix 13a	Disturbance History - Summary of Canadian Forest Inventories
  * Appendix 13b	Disturbance History - CAS Disturbance History Codes
  * Appendix 13c	Disturbance History - CAS Conversion
  * Appendix 14a	Wetland - Summary of Canadian Forest Inventories
  * Appendix 14b	Wetland - CAS Wetland Conversion
  * Appendix 14c	Wetland - CAS Wetland Codes
  * Appendix 15	Procedures for CAS Wetland Derivation
  * Appendix 16	Ecosite - Summary of Canadian Forest Inventories
  * Appendix 17	Sample of Export Procedure